Whittaker Models for Real Groups

### 2024-03-27 whittaker.tex
Wrote up the action of Q(R) on K-orbits, and the Cartan cohomology argument

%edited starting 8/27/17 for re-submission to Duke
\documentclass[10pt,leqno]{article}
\usepackage{verbatim}
\usepackage{amssymb}
\usepackage{mathtools}
%\usepackage{amsrefs}
\usepackage{rotating}
\usepackage{xcolor}
\usepackage{amsmath}
\usepackage{enumerate}
\usepackage[colorlinks=true, linktoc=page, citecolor=blue, linkcolor=blue, urlcolor=blue]{hyperref}

@@

\newcommand{\Gext}{\negthinspace\negthinspace\phantom{a}^\delta G}
\newcommand{\thetaG}{\negthinspace\negthinspace\phantom{a}^\theta
  G(\C)}
\newcommand{\thetaK}{\negthinspace\negthinspace\phantom{a}^\theta K(\C)}
\newcommand{\qed}{\hfill $\square$ \medskip}
\newenvironment{proof}[1][Proof]{\noindent\textbf{#1.} }{\qed}
\newcommand\exact[3]{1\rightarrow #1\rightarrow #2\rightarrow #3\rightarrow1}
\newcommand{\Aut}{\mathrm{Aut}}
\newcommand{\Inv}{\mathrm{Invol}}
\newcommand{\sgn}{\mathrm{sgn}}
\newcommand{\diag}{\mathrm{diag}}
\newcommand{\gr}{\mathrm{gr}}
\newcommand{\Out}{\mathrm{Out}}
\newcommand{\Int}{\mathrm{Int}}
\renewcommand{\int}{\mathrm{int}}
\newcommand{\Hom}{\mathrm{Hom}}
\newcommand{\kernel}{\mathrm{kernel}}
\newcommand{\Ad}{\mathrm{Ad}}
\newcommand{\zinv}{\mathrm{inv}}
\newcommand{\SRF}{\mathrm{SRF}}
\newcommand{\Gad}{G_\mathrm{ad}}
\newcommand{\Gsc}{G_\mathrm{sc}}
\newcommand{\Zsc}{Z_\mathrm{sc}}
\newcommand{\Ztor}{Z_\mathrm{tor}}
\newcommand{\Gbar}{\overline G}
\newcommand{\Kad}{K_\mathrm{ad}}
\newcommand{\Gal}{\mathrm{Gal}}
\newcommand{\Norm}{\mathrm{Norm}}
\newcommand{\Cent}{\mathrm{Cent}}
\newcommand{\Stab}{\mathrm{Stab}}
\newcommand{\I}{\mathcal I}
\renewcommand{\O}{\mathcal O}
\newcommand{\R}{\mathbb R}
\newcommand{\C}{\mathbb C}
\newcommand{\Z}{\mathbb Z}
\newcommand{\W}{\mathbb W}
\newcommand{\Ztwo}{\mathbb Z_2}
\newcommand{\N}{\mathcal N}
\newcommand{\Q}{\mathbb Q}
\newcommand{\E}{\mathbb E}
\newcommand{\G}{G}
\renewcommand{\H}{\mathbb H}
\newcommand{\h}{\mathfrak h}
\newcommand{\n}{\mathfrak n}
\renewcommand{\sl}{\mathfrak s\mathfrak l}
\renewcommand{\P}{\mathfrak p}
\renewcommand{\a}{\mathfrak a}
\newcommand{\zk}{\mathfrak z_\mathfrak k}
\newcommand{\A}{\mathbb A}
\newcommand{\K}{\mathcal K}
\newcommand{\B}{\mathcal B}
\renewcommand{\k}{\mathfrak k}
\newcommand{\spint}{\widetilde{Spin}}
\newcommand{\ch}[1]{#1^\vee}
\newcommand\sigmaqc{\sigma_{\text{qc}}}
\newcommand\thetaqc{\theta_{\text{qc}}}
\newcommand{\Fgal}{F_{\text{gal}}}
\newcommand{\Falg}{F_{\text{alg}}}
\newcommand{\cl}{\mathit{cl}}
\newcommand{\Lie}{\mathrm{Lie}}
\newcommand{\opp}{\text{-opp}}

\renewcommand{\t}{\mathfrak t}
\newcommand{\su}{\mathfrak s\mathfrak u}
\newcommand{\g}{\mathfrak g}
\newcommand\inv{^{-1}}
\newcommand\wh{\widehat}
\newcommand{\GL}{\text{GL}}
\newcommand{\SL}{\text{SL}}
\newcommand{\SO}{\text{SO}}
\newcommand{\SU}{\text{SU}}
\newcommand{\Spin}{\text{Spin}}
\newcommand{\chGGamma}{\phantom{a}^\vee G^\Gamma}
\newcommand{\GGamma}{G^\Gamma}
\newcommand{\s}{\mathfrak s}
\newcommand{\w}{\mathfrak w}
\newcommand{\AV}{\mathrm{AV}}
\newcommand{\WF}{\mathrm{WF}}
\newcommand{\AVann}{\mathrm{AV}_{\mathrm{ann}}}
\newcommand{\GK}{\mathrm{GK}}
\newcommand{\Op}{\O_p}
\newcommand{\Kostant}[1]{\mathcal{K}(#1)}

@@

\subsection{The group $Q(\R)$ and its actions} Let $Z=Z(G)$ be the center of $G$, and let $\Gad$ be the complex reductive group~$G/Z$.
Then $Z$ and $\Gad$ are defined over $\R$, and $Z(\R)$ is equal to the center of $G(\R)$. We may view~$\Gad(\R)$ as the set of inner automorphisms of~$G$ which are defined over~$\R$, and this contains the group $G(\R)_{\mathrm{ad}}=G(\R)/Z(\R)$ as a normal subgroup of finite index\footnote{AA 15-II-2024: is there a trivial way to explain why finite index?}
Define 
$$
Q(\R)=\Gad(\R)/G(\R)_{\mathrm{ad}}.
$$
This finite group may be viewed as a group of outer automorphisms of~$G(\R)$.

@@

\paragraph*{$\bullet$ Action on~(4)} The actions of $Q(\R)$ on (3) and (4) are quite similar, and the proof that they are simply transitive use an interpretation of $Q(\R)$ in terms of group cohomology.

We begin with the case of the wave-front set (4), because the underlying ideas in Galois cohomology may be more familiar to some readers.

To define the action of~$Q(\R)$ on~(4), first observe that~$\Gad$ acts on~$\g$ by the adjoint action. This action preserves~$\Op$, and the restriction to~$\Gad(\R)$ preserves~$\Op\cap (i\g(\R))$. Since elements on a given~$G(\R)_{\mathrm{ad}}$-orbit are in the same~$G(\R)$-orbit, this induces an action of $Q(\R)=\Gad(\R)/G(\R)_{\mathrm{ad}}$ on~$\Op\cap (i\g(\R))/G(\R)$.

\begin{proposition}
\begin{enumerate} 
\item The action of~$Q(\R)$ on $\Op\cap (i\g(\R))/G(\R)$ is simply transitive.
\item The map $\pi \mapsto \WF(\pi)$ is $Q(\R)$-equivariant.
\end{enumerate}
\end{proposition}

The proof of~(1) uses group comology, and we first recall some general notation. Let~$\Gamma$ be the Galois group~$\Z/2\Z$ of~$\R$. When~$A$ is a group and $\tau$ is an involutive automorphism of~$A$, we may consider the cohomology sets $H^0_\tau(\Gamma, A)$ and $H^1_\tau(\Gamma, A)$ attached to the action of~$\Gamma$ on~$G$ using~$\tau$.  These are pointed sets, and not groups in general if~$A$ isn't abelian. We may view $H^0_\tau(\Gamma, A)$ as the fixed-point-set $A^{\tau}$, and $H^1_\tau(\Gamma,A)$ as the quotient of $A^{-\tau} = \{ a \in A, a\tau(a)=1\}$ by the equivalence relation~$\sim$ generated by $a \sim x a \tau(x^{-1})$ for all $x \in G$.

@@

@@

For the proof of part~(2) of the proposition, use the asymptotic cone.

\paragraph*{$\bullet$ Action on~(3)} The action of~$Q(\R)$ on (3) is defined similarly, using the version of group cohomology attached to the Cartan involution~$\theta$. As above the exact sequence $1\rightarrow Z \rightarrow G \rightarrow \Gad\rightarrow 1$ 
gives rise to a long exact sequence of pointed sets
$$
1\rightarrow Z(\R) \rightarrow G(\R) \rightarrow \Gad(\R) \rightarrow H^1_\theta(\Gamma,Z)\rightarrow H^1_\theta(\Gamma,G)\rightarrow H^1_\theta(\Gamma,\Gad)
$$
and induces a canonical bijection $Q(\R) \simeq\kernel(H^1_\tau(\Gamma,Z)\rightarrow H^1_\tau(\Gamma,G))$ as in Lemma~\ref{l:Q}. We can use this to define an action of~$Q(\R)$ on $(\Op \cap \s)/K$: if~$X \in \Op \cap \s$ and we use the notation above, then by  \cite[Lemma 5.2]{galois} (applied using the Cartan involution~$\theta$ on~$G$, and the opposite of its differential on~$\mathfrak{s}$), the map
\begin{align*} (\Op \cap \s)/K & \to \kernel\left(H^1_\theta(\Gamma,\mathrm{Stab}_G(X))\rightarrow H^1_\theta(\Gamma,G)\right) \\ \mathrm{Ad}^\ast(g) \cdot X & \mapsto \text{class of $g^{-1} \theta(g)$ in $H^1_\theta(\Gamma,\mathrm{Stab}_G(X))$} \end{align*} is a bijection. Putting this together we get a simply transitive action of~$Q(\R)$ on~$(\Op \cap\s)/K$.
\footnote{AA 19-II-2023: should also say why the maps are equivariant. Is it obvious? At the moment I can't see it. We could always use Lemma~\ref{l:pi_to_av}.}

@@

\begin{proof} If we allow ourselves to use deep results, then this is a particular case of the main theorem of~\cite{SV1} (Theorem 1.4). In a perfect world, we could also give a more elementary argument, using the description of the Kostant--Sekiguchi correspondence in~\cite{galois} and the descriptions of the actions above; but  I'm not sure it's possible to do it without encountering a basepoint issue. Another possibility, suggested by Jeff, is to extract it from some arguments in Adams--Kaletha (e.g. the fact that $\WF(\pi)$ is the asymptotic cone of the $G(\R)$-orbit of the HC parameter of~$\pi$, or the connection with the Kostant section). \end{proof}

@@

There are several ways to describe this bijection.\footnote{AA 23-II-2024: it might be nice to mention the version with the asymptotic cone of the orbit of~$H_\pi$, which is extremely clean and concrete. } We choose to compose the maps (1)$\leftrightarrow$(3)$\leftrightarrow$(4).
Here is the conclusion.

@@

\begin{proposition}[\cite{adams_kaletha}]
Suppose $\pi$ is a generic discrete series representation. Then $\pi$ is $\w$-generic
for a unique Whittaker datum $\w$.
Write $\w=\w_X$ for some regular nilpotent element $X\in i\g(\R)$.
Then $H_\pi$ is $G(\R)$-conjugate to an element of the Kostant section of $X$.\footnote{AA 23-II-2024: would probably be useful to explain the connection with $\pi \mapsto \WF(\pi)$ in more detail...}
\end{proposition}

>>>>

%edited starting 8/27/17 for re-submission to Duke
\documentclass[10pt,leqno]{article}
\usepackage{verbatim}
\usepackage{amssymb}
\usepackage{mathtools}
%\usepackage{amsrefs}
\usepackage{rotating}
\usepackage{xcolor}
\usepackage{amsmath}
\usepackage{mathrsfs}
\usepackage{enumerate}
\usepackage[colorlinks=true, linktoc=page, citecolor=blue, linkcolor=blue, urlcolor=blue]{hyperref}

@@

\newcommand{\Gext}{\negthinspace\negthinspace\phantom{a}^\delta G}
\newcommand{\thetaG}{\negthinspace\negthinspace\phantom{a}^\theta
  G(\C)}
\newcommand{\thetaK}{\negthinspace\negthinspace\phantom{a}^\theta K(\C)}
\newcommand{\qed}{\hfill $\square$ \medskip}
\newenvironment{proof}[1][Proof]{\noindent\textbf{#1.} }{\qed}
\newcommand\exact[3]{1\rightarrow #1\rightarrow #2\rightarrow #3\rightarrow1}
\newcommand{\Aut}{\mathrm{Aut}}
\newcommand{\Inv}{\mathrm{Invol}}
\newcommand{\sgn}{\mathrm{sgn}}
\newcommand{\diag}{\mathrm{diag}}
\newcommand{\gr}{\mathrm{gr}}
\newcommand{\Out}{\mathrm{Out}}
\newcommand{\Int}{\mathrm{Int}}
\renewcommand{\int}{\mathrm{int}}
\newcommand{\Hom}{\mathrm{Hom}}
\newcommand{\kernel}{\mathrm{kernel}}
\newcommand{\Ad}{\mathrm{Ad}}
\newcommand{\ad}{\mathrm{ad}}
\newcommand{\zinv}{\mathrm{inv}}
\newcommand{\SRF}{\mathrm{SRF}}
\newcommand{\Gad}{G_\mathrm{ad}}
\newcommand{\Gsc}{G_\mathrm{sc}}
\newcommand{\Zsc}{Z_\mathrm{sc}}
\newcommand{\Ztor}{Z_\mathrm{tor}}
\newcommand{\Gbar}{\overline G}
\newcommand{\Kad}{K_\mathrm{ad}}
\newcommand{\Gal}{\mathrm{Gal}}
\newcommand{\Norm}{\mathrm{Norm}}
\newcommand{\Cent}{\mathrm{Cent}}
\newcommand{\Stab}{\mathrm{Stab}}
\newcommand{\I}{\mathcal I}
\renewcommand{\O}{\mathcal O}
\newcommand{\R}{\mathbb R}
\newcommand{\C}{\mathbb C}
\newcommand{\Z}{\mathbb Z}
\newcommand{\W}{\mathbb W}
\newcommand{\Ztwo}{\mathbb Z_2}
\newcommand{\N}{\mathcal N}
\newcommand{\Q}{\mathbb Q}
\newcommand{\E}{\mathbb E}
\newcommand{\G}{G}
\renewcommand{\H}{\mathbb H}
\newcommand{\h}{\mathfrak h}
\newcommand{\n}{\mathfrak n}
\renewcommand{\sl}{\mathfrak s\mathfrak l}
\renewcommand{\P}{\mathfrak p}
\renewcommand{\a}{\mathfrak a}
\newcommand{\zk}{\mathfrak z_\mathfrak k}
\newcommand{\A}{\mathbb A}
\newcommand{\K}{\mathcal K}
\newcommand{\B}{\mathcal B}
\renewcommand{\k}{\mathfrak k}
\newcommand{\spint}{\widetilde{Spin}}
\newcommand{\ch}[1]{#1^\vee}
\newcommand\sigmaqc{\sigma_{\text{qc}}}
\newcommand\thetaqc{\theta_{\text{qc}}}
\newcommand{\Fgal}{F_{\text{gal}}}
\newcommand{\Falg}{F_{\text{alg}}}
\newcommand{\cl}{\mathit{cl}}
\newcommand{\Lie}{\mathrm{Lie}}
\newcommand{\opp}{\text{-opp}}

\renewcommand{\t}{\mathfrak t}
\newcommand{\su}{\mathfrak s\mathfrak u}
\newcommand{\g}{\mathfrak g}
\newcommand\inv{^{-1}}
\newcommand\wh{\widehat}
\newcommand{\GL}{\text{GL}}
\newcommand{\SL}{\text{SL}}
\newcommand{\SO}{\text{SO}}
\newcommand{\SU}{\text{SU}}
\newcommand{\Spin}{\text{Spin}}
\newcommand{\chGGamma}{\phantom{a}^\vee G^\Gamma}
\newcommand{\GGamma}{G^\Gamma}
\newcommand{\s}{\mathfrak s}
\newcommand{\w}{\mathfrak w}
\newcommand{\AV}{\mathrm{AV}}
\newcommand{\WF}{\mathrm{WF}}
\newcommand{\AC}{\mathrm{AC}}
\newcommand{\AVann}{\mathrm{AV}_{\mathrm{ann}}}
\newcommand{\GK}{\mathrm{GK}}
\newcommand{\Op}{\O_p}
\newcommand{\Kostant}[1]{\mathcal{K}(#1)}

@@

\subsection{The group $Q(\R)$ and its actions} Let $Z=Z(G)$ be the center of $G$, and let $\Gad$ be the complex reductive group~$G/Z$.
Then $Z$ and $\Gad$ are defined over $\R$, and $Z(\R)$ is equal to the center of $G(\R)$. We may view~$\Gad(\R)$ as the set of inner automorphisms of~$G$ which are defined over~$\R$, and this contains the group $G(\R)_{\mathrm{ad}}=G(\R)/Z(\R)$ as a normal subgroup of finite index\footnote{AA 15-II-2024: is there a trivial way to explain why finite index?}.
Define 
$$
Q(\R)=\Gad(\R)/G(\R)_{\mathrm{ad}}.
$$
This finite group may be viewed as a group of outer automorphisms of~$G(\R)$.

@@

\paragraph*{$\bullet$ Action on~(4)} The actions of $Q(\R)$ on (3) and (4) are quite similar, and the proof that they are simply transitive use an interpretation of $Q(\R)$ in terms of group cohomology. 
We begin with the case of the wave-front set (4), because the argument a more familiar version of  Galois cohomology.

To define the action of~$Q(\R)$ on~(4), first observe that~$\Gad$ acts on~$\g$ by the adjoint action. This action preserves~$\Op$, and its restriction to~$\Gad(\R)$ preserves~$\Op\cap (i\g(\R))$. Since elements on a given~$G(\R)_{\mathrm{ad}}$-orbit are in the same~$G(\R)$-orbit, this induces an action of $Q(\R)=\Gad(\R)/G(\R)_{\mathrm{ad}}$ on~$\Op\cap (i\g(\R))/G(\R)$.

\begin{proposition}\label{prop:action_on_real_orbits}
\begin{enumerate} 
\item The action of~$Q(\R)$ on $\Op\cap (i\g(\R))/G(\R)$ is simply transitive.
\item The map $\pi \mapsto \WF(\pi)$ is $Q(\R)$-equivariant.
\end{enumerate}
\end{proposition}

The proof of~(1) uses group cohomology, and we first recall some general notation. Let~$\Gamma$ be the Galois group~$\Z/2\Z$ of~$\R$. When~$A$ is a group and $\tau$ is an involutive automorphism of~$A$, we may consider the cohomology sets $H^0_\tau(\Gamma, A)$ and $H^1_\tau(\Gamma, A)$ attached to the action of~$\Gamma$ on~$G$ using~$\tau$.  These are pointed sets, and not groups in general if~$A$ isn't abelian. We may view $H^0_\tau(\Gamma, A)$ as the fixed-point-set $A^{\tau}$, and $H^1_\tau(\Gamma,A)$ as the quotient of $A^{-\tau} = \{ a \in A, a\tau(a)=1\}$ by the equivalence relation~$\sim$ generated by $a \sim x a \tau(x^{-1})$ for all $x \in G$.

@@

An important point is that this action coincides with that defined before the statement of the Proposition. \textcolor{blue}{TODO: explain why. Basically the reason is that if we hit $X$ with $q_1q_2$ on the LHS of~\eqref{bij_q_2}, then then going through the definitions this goes to the element~$q_1q_2$ of~$Q(\R)$.}

@@

Part~(2) of the proposition is comes from general properties of the wavefront set in microlocal analysis, and from the fact that the action of $Q(\R)$ comes from automorphisms of~$G(\R)$. More precisely, if~$q$ is an element of~$Q(\R)$ and $\tilde{q}$ is a representative of~$q$ in $\Gad(\R)$, then the action of~$q$ on equivalence classes of $(\g, K)$-modules comes from the action of the automorphism $\mathrm{int}(\tilde{q})$ of~$G(\R)$ on $(\g, K)$-modules. Now the wavefront set of a distribution on a manifold satisfies general covariance properties under diffeomorphisms of the manifold: this follows from Hörmander's original definitions, see e.g. \cite[Section 2, p.~800]{HarrisHeOlafsson}. Applying this to the present situation, and going through the basics as in   \cite[Section 2]{HarrisHeOlafsson}, it immediately follows that $\pi \mapsto \WF(\pi)$ is equivariant under $Q(\R)$, and this concludes the proof of Proposition~\ref{prop:action_on_K_orbits}.

\paragraph*{$\bullet$ Action on~(3)} We turn to the action of~$Q(\R)$ on $(\Op \cap \s)/K$, and to the associated variety. For this it is convenient to use an isomorphic variant of~$Q(\R)$, defined in terms of~$K$ rather than~$G(\R)$.

Since the Cartan involution $\theta$ is an automorphism of~$G$, it preserves the center~$Z=Z(G)$, and induces an involution~$\theta_{\ad}$ of~$\Gad=G/Z$. Let $Z_K$ be the intersection $Z \cap K$, and let $K_{\ad}$ be the quotient $K/Z_K$. The natural map $K \mapsto \Gad$, induced by the inclusion $K \hookrightarrow G$, maps~$K$ to a subgroup of~$\Gad^{\theta_{\ad}}$, and has kernel~$Z_K$. Therefore it factors to an injective morphism $\iota\colon \Kad \hookrightarrow\Gad^{\theta_{\ad}} $. The image of~$\iota$ is a normal subgroup of~$\Gad^{\theta_{\ad}}$; using it we will identify $\Kad$ with a normal subgroup of $\Gad^{\theta_{\ad}}$. Define
\[ Q'(\R) = \Gad^{\theta_{\ad}}/\Kad.\]

\begin{lemma}\label{lem:q_and_qprime}
\begin{enumerate}
\item Every element of $Q(R)=\Gad(\R)/G(\R)_{\ad}$ has a $\theta_\ad$-invariant representative in $\Gad(\R)$.
\item Given $q \in Q(\R)$, and a $\theta_{\ad}$-invariant representative~$\tilde{q}$ of~$q$, the image of~$\tilde{q}$ in~$Q'(\R)$ depends only on~$q$ and not on the choice of~$\tilde{q}$. Denote this image by~$\Psi(q)$; then $q \mapsto \Psi(q)$ is an isomorphism between $Q(\R)$ and~$Q'(\R)$. 
\end{enumerate}
\end{lemma}

\begin{proof} \textcolor{red}{TODO!}\end{proof}

To define the  action of~$Q(\R)$ on $(\Op \cap \s)/K$, we point out that $Q'(\R)$ acts on $\Op \cap \s$ and that this action preserves the $K$-orbits. First, the adjoint action of~$\Gad$ on~$\g$ preserves both $\Op$ and~$\s$. Second, the action of~$K$ on $\Op \cap \s$ is trivial on~$Z_K$, and factors through an action of~$\Kad$. It is then easy to check that if two elements of $\Op \cap \s$ lie in on the same $\Kad$-orbit, then for every $g \in \Gad^{\theta_{\ad}}$, the elements  $\tilde{g} \cdot x$ and $\tilde{g} \cdot y$ lie on the same $\Kad$-orbit. This determines an action of~$Q'(\R)$ on~$(\Op \cap \s)/K$, and by Lemma~\ref{lem:q_and_qprime} we get an action of~$Q(\R)$ on~$(\Op \cap \s)/K$. This is the action featured in the following statement:

\begin{proposition}\label{prop:action_on_K_orbits}
\begin{enumerate} 
\item The action of~$Q(\R)$ on $(\Op \cap \s)/K$ is simply transitive.
\item The map $\pi \mapsto \AV(\pi)$ is $Q(\R)$-equivariant.
\end{enumerate}
\end{proposition}

The proof is similar to that of Proposition~\ref{prop:action_on_real_orbits}, but we need to use the version of Galois cohomology attached to the Cartan involution $\theta$. Taking up the above notation on Galois cohomology, the exact sequence $1\rightarrow Z \rightarrow G \rightarrow \Gad\rightarrow 1$ gives rise to a long exact sequence of pointed sets:
\begin{equation} \label{long_ptset_theta}
1\rightarrow Z_K \rightarrow K \rightarrow \Gad^{\theta_{\ad}} \rightarrow H^1_\theta(\Gamma,Z)\rightarrow H^1_\theta(\Gamma,G)\rightarrow H^1_{\theta_{\ad}}(\Gamma,\Gad).
\end{equation}
As in Lemma~\ref{l:Q}  this determines a bijection $Q'(\R) \leftrightarrow \kernel(H^1_\theta(\Gamma,Z)\rightarrow H^1_{\theta}(\Gamma,G))$. The argument for part~(1) of Proposition~\ref{prop:action_on_real_orbits} works seamlessly if we replace~$\sigma$ with~$\theta$, and proves that the action of~$Q'(\R)$ on $(\Op \cap \s)/K$ is simply transitive. Since the action of~$Q(\R)$ is defined by transport of structure from that of~$Q'(\R)$, this proves~(1).

As for~(2), it is again an immediate consequence of the precise definition of the associated variety. Stating this needs a little more care, since it is not obvious that $\Gad$ acts on representations of~$G(\R)$. However, the adjoint action of~$\Gad^{\theta_{\ad}}$ on $G$ preserves $K$; this this induces an action of~$\Gad^{\theta_{\ad}}$ on $(\g, K)$-modules. The restriction of that action to~$\Kad$ is trivial, and this gives an action of $Q'(\R)$ acts on equivalence classes of $(\g, K)$-modules. Now, the definition of the associated variety uses filtrations (see the Introduction of~\cite{vogan_bowdoin}) which are all invariant under $\Gad^{\theta_\ad}$, and inspecting the definitions it becomes clear that the map $\pi \mapsto \AV(\pi)$, taking a large discrete series $(\g,K)$-module  (or rather its equivalence class) to its associated variety, is equivariant under~$Q'(\R)$. In view of the relationship between the actions of $Q'(\R)$ and $Q(\R)$ on $(\Op \cap \s)/K$, this proves part~(2) of Proposition~\ref{prop:action_on_K_orbits}.
\qed

@@

\begin{proof} If we allow ourselves to use deep results, then this is a particular case of the main theorem of~\cite{SV1} (Theorem 1.4). In a perfect world, we could also give a more elementary argument, using the description of the Kostant--Sekiguchi correspondence in~\cite{galois} and the descriptions of the actions above; but  I'm not sure it's possible to do it without encountering a basepoint issue. Another possibility, suggested by Jeff, is to extract it from  arguments in Adams--Kaletha (e.g. the fact that $\WF(\pi)$ is the asymptotic cone of the $G(\R)$-orbit of the HC parameter of~$\pi$, and the connection with the Kostant section). \textcolor{red}{AA (27-III-2024): I think this last strategy should indeed work, but there are details to discuss with Jeff to complete the argument, and if everything turns out OK then  I'll write up the proof here.}\end{proof}

@@

There are several ways to describe this bijection.\footnote{AA 23-II-2024: I think we should mention the version with the asymptotic cone of the orbit of~$H_\pi$, which is extremely clean and concrete. } We choose to compose the maps (1)$\leftrightarrow$(3)$\leftrightarrow$(4).
Here is the conclusion.

@@

\begin{proposition}[\cite{adams_kaletha}]
Suppose $\pi$ is a generic discrete series representation. Then $\pi$ is $\w$-generic
for a unique Whittaker datum $\w$.
Write $\w=\w_X$ for some regular nilpotent element $X\in i\g(\R)$.
Then $H_\pi$ is $G(\R)$-conjugate to an element of the Kostant section of $X$.\footnote{AA 23-II-2024: would probably be useful to explain the connection with $\pi \mapsto \WF(\pi)$ in more detail...\\ AA 27-III-2024: furthermore, if the Kostant section is used in the proof that $\AV \leftrightarrow \WF$ coincides with Sekiguchi, then we should move this subsection to an earlier place, and then probably this discussion will have to be reworked.  }
\end{proposition}
